\begin{abstract}
We present MINT (Multi-participant Interactive Trading), a platform for experimental economics research enabling multi-participant trading sessions with role-based assignments. The system features event-driven architecture, session pool management, and integration of human participants with algorithmic traders. The platform implements lazy market creation that reduces resource consumption, WebSocket communication, and data collection across over 40 parameters. The system supports authentication methods including Prolific integration for research. MINT enables investigation of strategic interactions, information transmission, and market microstructure effects in experimental environments. The software is provided as open-source to encourage research community adoption.

\vspace{2cm}
This paper introduces the Multi-participant Interactive Trading (MINT) platform, a novel and versatile experimental environment for studying trading behaviour in continuous double-auction markets. Designed for researchers in experimental economics and finance, MINT supports both human–human and human–machine trading interactions, enabling flexible experimental treatments involving algorithmic traders. The platform is built using the Python programming language and ensures transparency, flexibility, and ease of customisation, allowing researchers to integrate custom trading algorithms and modify experimental parameters through an Administrative Interface Dashboard. MINT automatically records detailed Level 3 (L3) quote data, including all order submissions and message logs, facilitating comprehensive analyses of market and order book dynamics, as well as individual participant behaviour. The platform can also be easily integrated with participant recruitment services such as Prolific. Future developments will include enhanced front-end interfaces for real-time information display and GPT-based decision systems to explore AI-assisted trading behaviour.

\end{abstract}